R Notebook for MSDepression Project

### 2023-09-29 lab_notebook/lab_notebook.Rmd
Add files via upload

[] use different threshold of 
  [] 2.3
  [] 2.6
```{bash}
cd /Users/eballer/BBL/msdepression/templates/harvard_depression
#we are going to threshold the DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked.nii at 2.3 and 2.6
3dcalc -a DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked.nii -expr 'ispositive(a-2.3)' -prefix DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked_binarized_2_3.nii
3dcalc -a DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked.nii -expr 'ispositive(a-2.6)' -prefix DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked_binarized_2_6.nii

@@

>>>>

[x] use different threshold of 
  [x] 2.3
  [x] 2.6
```{bash}
cd /Users/eballer/BBL/msdepression/templates/harvard_depression
#we are going to threshold the DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked.nii at 2.3 and 2.6
3dcalc -a DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked.nii -expr 'ispositive(a-2.3)' -prefix DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked_binarized_2_3.nii
3dcalc -a DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked.nii -expr 'ispositive(a-2.6)' -prefix DepressionCircuit_t_resampled_to_mni_icbm152_asym09a_masked_binarized_2_6.nii

@@

[] a couple of other analyses
- people on Interferon B (11 total, 5 in nondepressed, 6 in depressed; solumedrol 2/2)
```{r}
table(dep_and_healthy_groups_for_ICD_analysis$depGroupVar[grep(pattern = "INTERF", x = dep_and_healthy_groups_for_ICD_analysis$Medication)])
```
- people on steroids (prednisone 1 in nondep, 1 in dep)
- 
```{r}
```
- people on ocrelizumab (17 in healthy group, 14 in depressed group)
```{r}
table(dep_and_healthy_groups_for_ICD_analysis$depGroupVar[grep(pattern = "OCRELIZUMAB", x = dep_and_healthy_groups_for_ICD_analysis$Medication)])
```

Could also do sensitivity analysis and remove the people on interferon Beta, prednisone, methylprednisolone
```{r}
dim(dep_and_healthy_groups_for_ICD_analysis %>% filter(!str_detect(Medication, 'INTERFERON|PREDNISON|METHYLPREDNISOLONE')))  #remove
